Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-14 paper_jasa.tex
made a few place marker comments on which to make changes later

The paper is organized as follows. Section \ref{sec:visual_test} defines terms as used in visual inference, and describes how to estimate the important quantities from experimental data. Section \ref{sec:regression} focuses on the application of  visual inference to linear models.  Section \ref{sec:simulation} describes the results of the three simulation experiments conducted to compare the power of the lineup protocol with the equivalent uniformly most powerful (UMP) and an analysis of the resulting data. The last section describes the next steps in this research.

@@

@@

>>>>

The paper is organized as follows. Section \ref{sec:visual_test} defines terms as used in visual inference, and describes how to estimate the important quantities from experimental data. The effect of the lineup size and number of observers on the power of the test is discussed in Section \ref{sec:size}. Section \ref{sec:regression} focuses on the application of  visual inference to linear models.  Section \ref{sec:simulation} describes the results of the three simulation experiments conducted to compare the power of the lineup protocol with the equivalent uniformly most powerful (UMP) and an analysis of the resulting data. The last section describes the next steps in this research.

@@

\green{Need to emphasize that this is important for the third experiment.}

@@

Experiment 3 does not have sensible $p$-values associated with each plot, so this assumption can only be tested with the first two experiments.
